\ttitle

### 2016-03-26 Chapters/Pre_Post_SIRS.tex
Layout changes
- Move tables and figures closer to where they are discussed in text
- Remove a few empty lines

\subsection{Statistics}

Continuous variables are reported as median (inter-quartile range).
Non-parametric tests were used to compare postoperative inflammatory markers (continuous data) with preoperative clinico-pathological characteristics (categorical data). 
Mann-Whitney U test was used when two categories were present and Kruskal-Wallis test was used when more than two categories were present.

@@

\clearpage
\section{Results}

@@

The relationship between preoperative clinico-pathological characteristics and postoperative C-reactive protein levels is shown in Tables \ref{table:sirs_crp} and \ref{table:sirs_crp_pvalues}).

\subsection{Preoperative vs. postoperative systemic inflammation}
The relationship between preoperative CRP and postoperative systemic inflammation is depicted graphically in Fig. \ref{fig:sirs_crp_crp} and Fig. \ref{fig:sirs_crp_alb} on page \pageref{fig:sirs_crp}.
The median CRP levels on the day of surgery and the first postoperative day (POD) were significantly higher in patients who had an elevated preoperative CRP. 
However, this association was not present after the first postoperative day.

@@

@@

\clearpage
%========================CRP vs Post-op SIRS============================================

%==============================================================================
\clearpage
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{Figures/sirs_crp_crp_alb}
	\caption{Relationship between preoperative CRP and postoperative CRP in the presence or absence of preoperative hypoalbuminemia.}
	\label{fig:sirs_crp_crp_alb}
\end{figure}
\input{Tables/sirs_crp_with_alb}
\clearpage
%==============================================================================

>>>>

\subsection{Statistics}
Continuous variables are reported as median (inter-quartile range).
Non-parametric tests were used to compare postoperative inflammatory markers (continuous data) with preoperative clinico-pathological characteristics (categorical data). 
Mann-Whitney U test was used when two categories were present and Kruskal-Wallis test was used when more than two categories were present.

@@

\section{Results}

@@

The relationship between preoperative clinico-pathological characteristics and postoperative C-reactive protein levels is shown in Tables \ref{table:sirs_crp} and \ref{table:sirs_crp_pvalues}.

\subsection{Preoperative vs. postoperative systemic inflammation}
The relationship between preoperative CRP and postoperative systemic inflammation is depicted graphically in Fig. \ref{fig:sirs_crp_crp} and Fig. \ref{fig:sirs_alb_crp} on page \pageref{fig:sirs_crp}.
The median CRP levels on the day of surgery and the first postoperative day (POD) were significantly higher in patients who had an elevated preoperative CRP. 
However, this association was not present after the first postoperative day.

@@

%======================== Pre-op factors vs Post-op CRP ============================================

\clearpage
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{Figures/sirs_crp_crp_alb}
	\caption{Relationship between preoperative CRP and postoperative CRP in the presence or absence of preoperative hypoalbuminemia.}
	\label{fig:sirs_crp_crp_alb}
\end{figure}
\input{Tables/sirs_crp_with_alb}
\clearpage
%==============================================================================

@@
